---
title: "Lecture Notes"
author: Luyun Ge
date: 2025-09-21
output: 
  github_document:
    toc: true
---
# Lecture 4 (Sep.16)
This lecture is about Data Wrangling - Data Import and Export
```{r message = FALSE}
library(tidyverse)
```
## Paths
* absolute path: the full address of file on computer; cons: not portable
```{r collapse = TRUE, message = FALSE}
litters_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_litters.csv")
#setwd() is also an absolute path
```
* relative path: directions to a file or folder from your current working directory; **portable**
```{r collapse = TRUE, message = FALSE}
litters_df_relative = 
  read_csv("../../data_import_examples/FAS_litters.csv")
# ../..	Two directories up from current working directory
```
## Update the names of variables in `litters_df` (to remove capital and space between)
```{r}
names(litters_df)
```
```{r collapse = TRUE}
litters_df = 
  janitor::clean_names(litters_df)
names(litters_df)
```
## Learning Assessment (CSV files)
Now importing the FAS_pups dataset:
```{r collapse = TRUE, message = FALSE}
pups_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_pups.csv", na = c("NA",".",""),skip = 3)
pups_df_relative = 
  read_csv("../../data_import_examples/FAS_pups.csv",na = c("NA",".",""),skip = 3)
```
```{r eval = FALSE, collapse = TRUE, message = FALSE}
# to view the data
skimr::skim(litters_df)
```
## Use function without downloading the whole package
`package`:`function`
```{r eval = FALSE, collapse = TRUE}
dplyr::filter
stats::filter
```
## Fixing the missing datas
```{r message = FALSE}
# na will treat "NA", ".", "" as missing values
litters_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_litters.csv", na = c("NA",".",""), skip = 10)
```
## Importing Data from EXCEL file
```{r}
mlb_df = 
  readxl::read_excel("../../data_import_examples/mlb11.xlsx")
```
If we only want part of columns
```{r}
words_df = 
  readxl::read_excel("../../data_import_examples/LotR_Words.xlsx", range = "B3:D6")
```
## Importing Data from SAS file
```{r collapse=TRUE}
pulse_df = 
  haven::read_sas("../../data_import_examples/public_pulse_data.sas7bdat")
names(pulse_df)
```
Clean the variable names:
```{r collapse=TRUE}
pulse_df = janitor::clean_names(pulse_df)
names(pulse_df)
```
## Data Export
```{r}
write.csv(words_df,"../../data_import_examples/words_df") 
```











