---
title: "Lecture Notes"
author: Luyun Ge
date: 2025-09-21
output: 
  github_document:
    toc: true
---
# Lecture 4 (Sep.16)
```{r}
library(tidyverse)
```
## Paths
* absolute path: the full address of file on computer; cons: not portable
```{r collapse = TRUE}
litters_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_litters.csv")
#setwd() is also an absolute path
```
* relative path: directions to a file or folder from your current working directory; **portable**
```{r collapse = TRUE}
litters_df_relative = 
  read_csv("../../data_import_examples/FAS_litters.csv")
# ../..	Two directories up from current working directory
```
```{r}
names(litters_df)
```
## Update the names of variables in `litters_df` (to remove capital and space between)
```{r collapse = TRUE}
litters_df = 
  janitor::clean_names(litters_df)
names(litters_df)
```
## Learning Assessment
Now importing the FAS_pups dataset:
```{r collapse = TRUE}
pups_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_pups.csv", na = c("NA",".",""),skip = 3)
pups_df_relative = 
  read_csv("../../data_import_examples/FAS_pups.csv",na = c("NA",".",""),skip = 3)
```
```{r eval = FALSE, collapse = TRUE}
# to view the data
skimr::skim(litters_df)
```
## Use function without downloading the whole package
`package`:`function`
```{r eval = FALSE, collapse = TRUE}
dplyr::filter
stats::filter
```
## Fixing the missing datas
```{r}
litters_df = 
  read_csv("~/Desktop/Fall2025/P8105 DS I/data_import_examples/FAS_litters.csv", na = c("NA",".",""), skip = 10)
```

